The past and future of visualization for computing in science and engineering

### 2020-03-27 CombaWeiskopf2020/paper.tex
fix latex errors and wide figures
move intro blurb to abstract

@@

\author{%
	Joao Comba, Daniel Weiskopf
	\IEEEcompsocitemizethanks{
	\IEEEcompsocthanksitem Joao Comba is at Universidade Federal do Rio Grande do Sul, Brazil\protect\\ 
	\IEEEcompsocthanksitem Daniel Weiskopf is at University of Stuttgart, Germany.
}

\IEEEtitleabstractindextext{%
\begin{abstract}
We provide a retrospective of the Visualization Corner and how its articles covered visualization topics since 2011. This leads us to identify current and future developments in visualization research and their impact on computing in science and engineering.
\end{abstract}
}

@@

The Visualization Corner (VizCorner) is a long-standing department in IEEE Computing in Science \& Engineering (CiSE). It reflects the long-term and fruitful overlap between computer-based visualization and computational science and engineering. As early as 1987, the Workshop on Visualization in Scientific Computing identified the need for visualization for the growing area of simulation-oriented science~\cite{NSFreport1987}. In general, visualization has been playing a great role in visual data analysis and communication in science, engineering, and beyond.

Let us first focus on the scope of the VizCorner by looking into what we have covered there in the last decade. Then we will relate this to current trends in visualization research, leading to possible future developments for visualization in science and engineering.

@@

The VizCorner has three column articles per year on average. Our goal is to cover the breadth of visualization research and practice relevant to the readers of this magazine. Therefore, the VizCorner wants to provide a glimpse of basic visualization research questions but also illustrate and highlight the practical impact of visualization. We have been soliciting papers mostly from the visualization community in order to bring in their perspective to the various areas of computational science and engineering.

Let us organize the papers from 2011 until now into themes, indicating the focal areas of the VizCorner. 
We will provide examples of previous papers that illustrate the breadth of visualization possibilities.

@@

\begin{figure}[H]
    \begin{center}    
        \includegraphics[width=0.9\textwidth]{simvis.png}
        \caption{Example of multivariate data visualization with the SimVis system~\cite{Doleisch2012}. This screenshot shows the windflow around a building, where turbulent parts are emphasized using a vortex detection method. Image: \copyright{} 2012 IEEE, reprinted from Doleisch and Hauser~\cite{Doleisch2012}.
  \label{fig:simvis}}        
    \end{center}
\end{figure}

@@

\begin{figure}[th]
	\begin{center}	
		\includegraphics[width=0.9\textwidth]{karman_weno3.png}
		\caption{Computational dye advection~\cite{Karch2012}, applied to a 2D simulation of a von K{\'a}rm{\'a}n vortex street. Image: \copyright{} 2012 IEEE, reprinted from Karch et al.~\cite{Karch2012}.
  \label{fig:karman}}		
	\end{center}
\end{figure}

@@

\begin{figure}[th]
    \begin{center}    
        \includegraphics[width=0.55\textwidth]{museum1.png} \hspace{-3em} \raisebox{12ex}{\includegraphics[width=0.5\textwidth]{museum2.png}}
        \caption{Interactive table with a plankton visualization. Image: \copyright{} 2016 IEEE, reprinted from Sauer et al.~\cite{Sauer2016}. TODO for layout: could you place the right image slightly overlapping on the left on? As to imply something similar to an inset?
  \label{fig:museum}}        
    \end{center}
\end{figure}

@@

\begin{figure}[H]
    \begin{center}    
        \includegraphics[width=0.9\textwidth]{galaxies.png}
        \caption{Virtual flight through the universe. 
 Image: \copyright{} 2015 IEEE, reprinted from Aragon-Calvo and SubbaRao~\cite{Aragon-Calvo2015}.
  \label{fig:galaxies}}        
    \end{center}
\end{figure}

@@

\bibliographystyle{IEEEtran}
\bibliography{refs}

>>>>

\usepackage{cite}
\usepackage[pdftex]{graphicx}

@@

\author{%
	Joao Comba, Daniel Weiskopf
	\IEEEcompsocitemizethanks{
	\IEEEcompsocthanksitem Joao Comba is at Universidade Federal do Rio Grande do Sul, Brazil\protect\\ 
	\IEEEcompsocthanksitem Daniel Weiskopf is at University of Stuttgart, Germany.
}}

\IEEEtitleabstractindextext{%
\begin{abstract}
A retrospective of the Visualization Corner (VizCorner) since 2011 leads us to identify current and future developments in visualization research and their impact on computing in science and engineering.
The VizCorner department of CiSE reflects the long-term and fruitful overlap between computer-based visualization and computational science and engineering. As early as 1987, the Workshop on Visualization in Scientific Computing identified the need for visualization for the growing area of simulation-oriented science~\cite{NSFreport1987}. Visualization now plays a key role in visual data analysis and communication in science, engineering, and beyond. 
Looking into what we have covered in VizCorner for the last decade, we connect with current trends in visualization research, leading to possible future developments for visualization in science and engineering.
\end{abstract}
}

@@

@@

The goal of the VizCorner is to cover the breadth of visualization research and practice relevant to the readers of this magazine. We provide a glimpse of basic research questions and highlight the practical impact of visualization.
Organizing the papers from 2011 until now into themes highlights the focal areas of the VizCorner, 
and illustrates the breadth of visualization possibilities.

@@

\begin{figure*}
    \begin{center}    
        \includegraphics[width=0.9\textwidth]{simvis.png}
        \caption{Example of multivariate data visualization with the SimVis system~\cite{Doleisch2012}. This screenshot shows the windflow around a building, where turbulent parts are emphasized using a vortex detection method. Image: \copyright{} 2012 IEEE, reprinted from Doleisch and Hauser~\cite{Doleisch2012}.
  \label{fig:simvis}}        
    \end{center}
\end{figure*}

@@

\begin{figure*}
	\begin{center}	
		\includegraphics[width=0.9\textwidth]{karman_weno3.png}
		\caption{Computational dye advection~\cite{Karch2012}, applied to a 2D simulation of a von K{\'a}rm{\'a}n vortex street. Image: \copyright{} 2012 IEEE, reprinted from Karch et al.~\cite{Karch2012}.
  \label{fig:karman}}		
	\end{center}
\end{figure*}

@@

\begin{figure*}
    \begin{center}    
        \includegraphics[width=0.55\textwidth]{museum1.png} \hspace{-3em} \raisebox{12ex}{\includegraphics[width=0.5\textwidth]{museum2.png}}
        \caption{Interactive table with a plankton visualization. Image: \copyright{} 2016 IEEE, reprinted from Sauer et al.~\cite{Sauer2016}. TODO for layout: could you place the right image slightly overlapping on the left on? As to imply something similar to an inset?
  \label{fig:museum}}        
    \end{center}
\end{figure*}

@@

\begin{figure*}
    \begin{center}    
        \includegraphics[width=0.9\textwidth]{galaxies.png}
        \caption{Virtual flight through the universe. 
 Image: \copyright{} 2015 IEEE, reprinted from Aragon-Calvo and SubbaRao~\cite{Aragon-Calvo2015}.
  \label{fig:galaxies}}        
    \end{center}
\end{figure*}

@@

\bibliographystyle{IEEEtran}
\bibliography{./refs}

\bigskip
